Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-13 review_article.Rmd
Fix quotes

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
fontsize: 11pt
link-citations: yes
fig_caption: yes
biblio-style: vancouver
yolo: yes
---

@@

## Public face

@@

## Cartograms

@@

>If, for instance, it is desirable that areas on a map have boundaries which are as simple as possible, why not draw the areas as simple shapes in the first place?

@@

>designing a map tailored to precise goals [is] easier than forcing a single map to accommodate diverse objectives - @CPISACA

@@

> 'Where control of the message is important, static maps will continue to be the most effective, although good tables, graphs, and explanatory text are still needed in order to ensure that different people will see the same thing in the maps' @CPISACA

>>>>

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
fontsize: 11pt
link-citations: yes
fig_caption: yes
biblio-style: vancouver
yolo: yes
---

@@

## Publicly available atlases using choropleth methods

@@

## Cartograms as an alternative display

@@

>"If, for instance, it is desirable that areas on a map have boundaries which are as simple as possible, why not draw the areas as simple shapes in the first place?"

@@

>"designing a map tailored to precise goals [is] easier than forcing a single map to accommodate diverse objectives" @CPISACA

@@

>"Where control of the message is important, static maps will continue to be the most effective, although good tables, graphs, and explanatory text are still needed in order to ensure that different people will see the same thing in the maps" @CPISACA
